Robustly decorrelating errors with mixed quantum gates

### 2020-03-05 decorrelation/mixed_unitaries.tex
all the email updates and the sparsity updates should be on the tex file. The arxiv folder is no longer faithful to arxiv version v1

Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}. In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step. While Pauli Frame Randomization shares the some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{1q_robustness_delta.pdf}
  \caption{\textbf{One-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error. The target is an $X_{\pi/2}$ gate on a single qubit. The generator-exact MQG dramatically outperforms both the robust generator-exact and any of the bare unitaries at $\delta=0$. However, even a relatively small amplitude error leads to a regime in which the the robust generator-exact will yield the better gate. Similar results are obtained for drift in the qubit frequency.}
  \label{fig:YMQG}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2q_robustness.pdf}
  \caption{\textbf{Two-qubit robust generator-exact MQG} Numerical results showing the the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude). It is intended to model a pair of qubits interacting via resonant exchange. Both MQGs can be seen to outperform the bare unitary control over a wide range of detunings. The robust generator-exact  MQG always outperforms the generator-exact MQG, and both MQGs outperform any of the bare unitary controls over a wide range of detunings. Similar results are obtained for drift in the qubit control amplitude.}
  \label{fig:2MQG}
\end{figure}

>>>>

Randomized protocols have a long history of outperforming their deterministic counterparts\cite{Viola2005, Santos2006}. In circuit models, Pauli Frame Randomization \cite{Wallman2016, 1803.01818, dahlen2018experimental} has been shown to reduce coherent errors by introducing randomness in a pre-compilation step. While Pauli Frame Randomization shares some favorable properties with MQGs, we will see that MQGs additionally admit a hardware-efficient implementation and numerous useful modifications when they are posed as a numerical optimization problem.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{1q_robustness_delta.pdf}
  \caption{\textbf{One-qubit robust generator-exact MQG} Numerical results showing the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a the fractional amplitude error. The target is an $X_{\pi/2}$ gate on a single qubit. The generator-exact MQG dramatically outperforms both the robust generator-exact and any of the bare unitaries at $\delta=0$. However, even a relatively small amplitude error leads to a regime in which the robust generator-exact will yield the better gate. Similar results are obtained for drift in the qubit frequency.}
  \label{fig:YMQG}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2q_robustness.pdf}
  \caption{\textbf{Two-qubit robust generator-exact MQG} Numerical results showing the diamond distance errors for a generator-exact MQG (dashed blue), a robust generator-exact MQG (solid orange), and a large set of bare unitary controls (thin solid grey) as a function of a spurious detuning (quantified by the ratio of the detuning to the maximum control amplitude). It is intended to model a pair of qubits interacting via resonant exchange. Both MQGs can be seen to outperform the bare unitary control over a wide range of detunings. The robust generator-exact  MQG always outperforms the generator-exact MQG, and both MQGs outperform any of the bare unitary controls over a wide range of detunings. Similar results are obtained for drift in the qubit control amplitude.}
  \label{fig:2MQG}
\end{figure}
